\documentclass{report}

\usepackage{listings}
\usepackage{color}

\begin{document}

\title{Image manipulation - in theoretical approach}

\author{Hamid Mirisaee,
\and Jander Nascimento, 
\and Raquel Oliveira}

\maketitle

\begin{abstract}

We should write our abstract here..

\end{abstract}

\tableofcontents

\vfill

\section{Image type}

	\subsection{PNG}

		\textit{Fill me}.

	\subsection{JPG}

		\textit{Fill me}.

	\subsection{GIF}

		\textit{Fill me}.

	\subsection{PNM}

		\textit{Fill me}.

\section{Filters}

	\subsection{Fundamental}

		\textit{Fill me}.

		\subsubsection{Convolution}

			\textit{Fill me}.

		\subsubsection{Kernel}

			\textit{Fill me}.

	\subsection{Used filters}
		
		\subsubsection{Gradient}

			\textit{Fill me}.
		
		\subsubsection{Mean}

			\textit{Fill me}.

		\subsubsection{Gaussian}

			\textit{Fill me}.

		\subsubsection{Laplacian}

			\textit{Fill me}.

\section{Color space}          

	\subsection{RGB}
		
		\textit{Fill me}.

	\subsection{CYMK}

		\textit{Fill me}.

	\subsection{Gray scale conversion}

		\textit{Fill me}.

\section{Cropping}

	\textit{Fill me}.

\section{Fusion}

	\textit{Fill me}.

\section{Resizing}

	Image resizing consist in convert an image to a size in which may or not respect the previous ratio.
	When dealing with reducing the size of an image is quite simple to do it, but when dealing with enlarging 
	the image, we have problems with unknown pixels. Too fast?
	When we stretch an image, we have few known pixels (dots which are image composition, think like the cells of a human being).

	There is a lot of algorithms that helps to guess (fill the gaps) those unknow pixels. for instance:

	\begin{itemize}
	  \item Nearest neighbor
	  \item Linear interpolation
	  \item Bilinear interpolation
	  \item Bicubic interpolation
	\end{itemize}

	The simplest algorithm, nearest neighbor, simply copy the color intensity of the neighbor pixels. But the results are not quite good since 
	the images get squared.
	The adopted algorithm is, \textbf{Bilinear interpolation},  due its speed and simplicity.

\section{Histogram}

	\subsection{Color histogram}

		\textit{Fill me}.

	\subsection{Histogram stretching}

		\textit{Fill me}.

\end{document}
